---
title: "data-replication-assignment"
format: html
editor: visual
---

## Specialist predation covaries with colour polymorphism
in tawny owls

Summary:

This paper is looking at heritable color polymorphism (aka feather color) in tawny owls, and how that is different between tawny owls that specialize to a specific prey type, and those that hunt more generally among all prey types. They hypothesized that the grey morph is more specialised in mammalian prey than the brown morph, because of the advantage that those color morphs lend the owl for hunting in boreal vs temperate conditions, and the prey available in those areas. They conclude, based upon the below data, that the brown polymorph is more generalistic (eats a wider variety of prey types) than the grey polymorph, which would be advantageous in unpredictable environments.

Dataset:

The dataset shared represents Tawney owls from Uusimaa, in an area that has agricultural land, spruce-dominated and mixed forests and lakes and streams.\~100 nest boxes were placed, and they were visited 3-5 times to observe clutch size, timing of hatching and hatching success. Plumage colour was scored in adults using a semi-continuous score based on the degree of reddish-brown colouration in four body parts: facial disc, back, breast and general appearance, and the owl was categorized as generally a grey or brown morph. They then cleaned the floor of the nest boxes and recorded what prey bones were present in the owl pellets found in that nest. This yielded them 38 nets where both parents and all nestling were observed. To estimate mass of all prey, they multiplied the average mass of that prey by the number of items of that prey count that they observed in the nest. They also sampled the amount of small mammals in the areas observed to observe the abundance of prey that were available to hunt for the owls.

What I'm replicating:

I will be replicating:

Figure 1: "The inverse Simpson’s diversity index of the prey items delivered by grey and brown fathers in relation to small mammal density index. A high value indicates high diversity (number and evenness) of prey types. The plot presents the marginal effects (± 95% CI) of the interaction in the statistical model"

Figure 2: "Proportion of mammalian prey mass delivered to the nest by grey and brown fathers in relation to small mammal density index. The plot presents the marginal effects (± 95% CI) of the interaction in the statistical model"

[**Code:**]{.underline}

Read in the data table (from the text file given on Dryad)

```{r}
# Read the preydiet_TO.txt file into a dataframe
f <- "preydiet_TO.txt"
d <- read.table(f, header = TRUE, sep = "\t")

head(d)

```

**Table 1:**

Conducting an LMM of variation in inverse Simpson’s diversity index among prey items delivered to the nest in relation to paternal colour morph, small mammal index, brood size and the interaction paternal colour morph by small mammal index

```{r}
version

install.packages("Matrix", type = "source")
.rs.restartR()  # For RStudio

```

```{r}
install.packages("lme4", type = "source")
.rs.restartR()  # For RStudio
```

```{r}
#installing lme4 package to conduct an LMM
install.packages("Matrix")
install.packages("lme4")

install.packages("Matrix", type = "source")
install.packages("lme4", type = "source")


packageVersion("lme4")
packageVersion("Matrix")
```

```{r}
library(Matrix)
library(lme4)

# Fitting the LMM
m_SDI <- lmer(inv_Simpson_index ~ male_morph * autumn_voles + brood_size + (1 | maleID) + (1 | year), data = d)

```

**Figure 1:**

What's listed in the methods:
